---
title: "MICS6 - 10 - WS.1.1"
author: "Reid Minto"
date: "March 25, 2020"
output:
  word_document: default
  html_document: default
always_allow_html: true
---

# Load libraries



```{r, warning = F, message = F}

library(tidyverse); library(haven); library(lubridate);
library(knitr); library(kableExtra)
library(Hmisc); library(survey)
library(expss); library(here); library(gmodels)

library(tableone); library(sjPlot); library(srvyr)

```
 
# Import data

`here` function navigates you to top level Rproj directory



```{r}
# haven library called above has read_sav function for reading in .sav / .sps etc
# files from other languages
here()
hh <- read_sav(here("Data/Tunisia_hh.sav"))
# hh <- as_factor(hh, only_labelled = TRUE)




```

Filter only cases where hh interview = 1, create a variable `hhweightHH48` by multiplying 
`HH48` and `hhweight`, number of hh members by sample weight


Note: this is just first pass rough draft / run through - much of this looks like it can be consolidated into a single chunk / a single function execute per section from what I've seen so far, but broken up in first pass

```{r}

hh <- hh %>% filter(HH46 == 1) %>%
  mutate(hhweightHH48 = HH48 * hhweight,
         nhhmem = 1)


```

Include `MICS6 - 10 - WS.sps` is called



```{r}


hh <- hh %>% 
  mutate(drinkingWater = ifelse(WS1 %in% c(11:14, 21, 31, 41, 51, 
                                           61, 71, 72, 91, 92), 1, 2))

# `casewhen` cleaner than nested chains of ifelse for >2 conditions
# same as SQL 'case when', but TRUE ~ val acts in place of "else"
hh <- hh %>%
  mutate(toiletType = case_when(
    WS11 %in% c(11:13, 18, 21, 22, 31) ~ 1,
    WS11 == 95 ~ 3,
    TRUE ~ 2
  ))
  


hh <- hh %>% mutate(flush = NA) %>% 
  mutate(flush = ifelse(WS11 %in% c(11:14, 18), 1, flush))



hh = hh %>% mutate(sharedToilet = case_when(
  WS17 %in% c(1:5) ~ 1,
  WS17 %in% 97:99 ~ 9,
  is.na(WS17) ~ 0,
  TRUE ~ 2))
hh = hh %>% mutate(sharedToilet = ifelse(WS16 == 2, 3, sharedToilet))


# visual check
aa = hh %>% select(WS1, HH1, HH2, nhhmem, hhweightHH48, hhweight, HH48, stratum, PSU, drinkingWater, WS11)

```



After 10-WS include file call, resume



```{r}

hh <- hh %>% 
  mutate(improvedWater = ifelse(drinkingWater == 1, 100, 0),
         total = 1,
         total100 = 100)




```




# All Value labels

Variable and Value labels all at once

Question if this is necessary at all in R, b/c can just as easily label R tables / figured with a list of labels when generating the tables / figures / reports, avoiding doing as we go along. 



```{r}

hh <- hh %>% apply_labels(
  nhhmem = "Number of household members",
  WS1 = c(
  "Tanker Truck" = 61, 
  "Cart with small tank" = 71, 
  "Bottled water [A]" = 91,  
  "Sachet water [A]" = 92, 
  "Missing" = 99),
  
  
  drinkingWater = "Main Source of drinking water",
  drinkingWater = c(
    "Improved sources" = 1,
    "Unimproved sources" = 2
    ),
  toiletType = "Type of sanitation facility",
  toiletType = c(
    "Improved" = 1,
    "Unimproved" = 2,
    "Open defecation (no facility, bush, field)" = 3
    ),
  flush = "Flush/Pour flush to:",
  sharedToilet = c(
    "Not shared" = 0,
    "5 households or less" = 1,
    "More than 5 households" = 2,
   "Public facility" = 3,
   "DK/Missing" = 9
  ),
  improvedWater = "Percentage using improved sources of drinking water [1]",
  HH6 = c("URBAN" = 1, "RURAL" = 2),
  WS1 = ""
  
  
  )




# hh <- as_factor(hh, only_labelled = TRUE)






```


# Tables


* Note - lots of understanding and formatting etc to get through on tables


explore expss package which seems to have capability to produce `ctables` 
equivalents




```{r ,echo=FALSE, message=FALSE, warnings=FALSE, results = 'asis'}

#################    URGENT   ######################
# find why tabulation plan excel sheet columns don't correspond to spss value labels

# other ws1 values not mapped to columns in tabulation plan?
hh.tab <- hh %>% select(HH1, WS1, total, HH6, HH7, helevel,
                        windex5, drinkingWater, total100,
                        improvedWater, nhhmem, toiletType, sharedToilet,
                        flush, hhweight, hhweightHH48) %>% 
  filter(WS1 %in% c(61, 71, 91, 92, 99)) 
  
hh.tab = as_factor(hh.tab, only_labelled = TRUE)

#tabl = CrossTable(hh.tab$HH6 , hh.tab$WS1, prop.r = TRUE, 
#                  digits = 3, missing.include = FALSE)

#tabl <- table(as_factor(hh.tab$HH6), as_factor(hh.tab$WS1))

#tabl <- table(hh.tab$HH6, hh.tab$WS1)

kable(table(hh.tab$HH6, hh.tab$WS1), format = "html", digits = 3, row.names = TRUE) %>% 
  kable_styling(bootstrap_options = c("striped" , "bordered"), 
                font_size = 13, full_width = F)



```




## Test table packages

After lots of exploring for table producing,
`expss` package in R seems most promising, as it seems to have direct ability to produce any `ctable` from SPSS

Much formatting to be done

```{r, results= 'asis'}

#hh.tab %>% as_factor(only_labelled = TRUE) %>% 
#  as_survey(weights = c(hhweightHH48)) %>%
#  group_by(HH6, WS1, nhhmem) %>%
#  summarize(n = survey_total()) %>%
#  spread(WS1, n) %>% 
#  kable(format = "html", digits = 3, row.names = TRUE) %>% 
#  kable_styling(bootstrap_options = "striped", font_size = 12, full_width = F)


hh.tab = as_factor(zap_labels(hh.tab), only_labelled = TRUE)

#CrossTable(hh.tab$HH6, hh.tab$WS1, expected = FALSE, prop.col = FALSE, prop.r = TRUE, 
#           prop.t = F, prop.chisq = F, chisq = F) %>% 
#  kable(format = "html", digits = 3, row.names = TRUE) %>% 
#  kable_styling(bootstrap_options = "striped", font_size = 12, full_width = F)



#tabl = CrossTable(hh.tab$HH6, hh.tab$WS1, expected = FALSE, 
#                  prop.col = FALSE, prop.r = TRUE, 
#           prop.t = F, prop.chisq = F, chisq = F, max.width = 2)[[2]]

#tabl %>%  kable(format = "html", digits = 3, row.names = TRUE) %>% 
#  kable_styling(bootstrap_options = "striped", font_size = 12, full_width = F)

calculate(hh.tab, cro_rpct(HH6, list(total(), WS1), 
                           total_statistic = "u_cases")) %>% 
  kable(format = "html", digits = 3, row.names = TRUE) %>% 
  kable_styling(bootstrap_options = "striped", font_size = 12, full_width = F)



```

