---
title: "Ch10 - WS 1.1 - 1.3"
author: "Reid Minto"
date: "April 22, 2020"
output: word_document
always_allow_html: true
---



1. Producing two more tables: ws1.2 and ws1.3 as well

2. Integrate in the code suppression and parenthesizing rules:
  a. Where the unweighted count of the denominator is less than 25 cases the value should be suppressed and replaced with an asterisk *
  b. Where the unweighted count is between 25-49 the values should be parenthesized ().
 

3. Compile the three tables’ scripts into 1 markdown that can produce an SFR chapter (albeit for only 3 tables) in word document

a. It will be paramount here that the table formatting in the original SFR reports are maintained.

```{r, warning = F, message = F}

library(tidyverse); library(haven); library(lubridate);
library(knitr); library(kableExtra);
library(Hmisc); library(survey)
library(expss); library(here); library(gmodels)
library(flextable); library(formattable)
library(prettydoc); library(officer)

library(tableone); library(sjPlot); library(srvyr)

```
 
# Import data

`here` function navigates you to top level Rproj directory



```{r}
# haven library called above has read_sav function for reading in .sav / .sps etc
# files from other languages
here()
hh <- read_sav(here("Data/Tunisia_hh.sav"))
# hh <- as_factor(hh, only_labelled = TRUE)




```

Filter only cases where hh interview = 1, create a variable `hhweightHH48` by multiplying 
`HH48` and `hhweight`, number of hh members by sample weight


Note: this is just first pass rough draft / run through - much of this looks like it can be consolidated into a single chunk / a single function execute per section from what I've seen so far, but broken up in first pass




# 10 - WS.1.1

```{r}

hh <- hh %>% filter(HH46 == 1) %>% 
  mutate(hhweightHH48 = HH48 * hhweight) %>% mutate(nhhmem = 1 * hhweightHH48)

var_lab(hh$nhhmem) = "Number of household members"; val_lab(hh$nhhmem) = make_labels("
                                                                                     1
                                                                                     ")



var_lab(hh$WS1) = "Source principale d'eau de boisson"
val_lab(hh$WS1) = make_labels("
    11 DANS LE LOGEMENT
    12 DANS LA CONCESSION/JARDIN/ PARCELLE
    13 CHEZ LE VOISIN
    14 ROBIENT PUBLIC/BORNE FONTAINE
    21 PUITS A POMPE/FORAGE
    31 PROTEGE
    32 PAS PROTEGE
    41 SOURCE PROTEGEE
    42 SOURCE NON PROTEGEE
    51 EAU DE PLUIE
    61 CAMION CITERNE
    71 CHARRETTE AVEC PETITE CITERNE
    81 EAU DE SURFACE (RIVIERE, BARRAGE, LAC, MARE, COURANT, CANAL, SYSTEME D’IRRIGATION)
    91 EAU EN BOUTEILLE
    92 EAU EN SACHET
    96 AUTRE
    99 NON REPONSE
                                 ")
############   Begin 10 - WS.sps   ############################

hh <- hh %>% 
  mutate(drinkingWater = ifelse(WS1 %in% c(11:14, 21, 31, 41, 51, 61, 71, 72, 91, 92), 1, 2))

var_lab(hh$drinkingWater) = "Main source of drinking water"
val_lab(hh$drinkingWater) = make_labels("
  1 Improved sources
  2 Unimproved sources
")



hh <- hh %>% 
  mutate(toiletType = case_when(
    WS11 %in% c(11:13, 18, 21, 22, 31) ~ 1,
    WS11 == 95 ~ 3,
    TRUE ~ 2
  ))


var_lab(hh$toiletType) = "Type of sanitation facility"
val_lab(hh$toiletType) = make_labels("
    1 Improved
    2 Unimproved
    3 Open defecation (no facility, bush, field)
                                     ")


hh <- hh %>% mutate(flush = NA) %>% mutate(flush = case_when(
  WS11 %in% c(1:14, 18) ~ 1
))

var_lab(hh$flush) = ""; val_lab(hh$flush) = make_labels(" 
                                                        1 Flush/Pour flush to:
                                                        ")



hh <- hh %>% mutate(sharedToilet = case_when(
  WS17 %in% c(1:5) ~ 1,
  WS17 %in% 97:99 ~ 9,
  NA ~ 0,
  TRUE ~ 2
))

hh <- hh %>% mutate(sharedToilet = ifelse(WS16 == 2, 3, sharedToilet))

var_lab(hh$sharedToilet) = " "
val_lab(hh$sharedToilet) = make_labels("
  0 Not shared
  1 5 households or less
  2 More than 5 households
  3 Public facility
  9 DK/Missing
                                       ")


############   End 10 - WS.sps   ############################


hh <- hh %>% mutate(improvedWater = ifelse(drinkingWater == 1, 100, 0)) 


var_lab(hh$improvedWater) = "Percentage using improved sources of drinking water [1]"
var_lab(hh$WS1) = ""


hh <- hh %>% mutate(total = 1, total100 = 100)
var_lab(hh$total) = "Total"; var_lab(hh$total100) = "Total"
val_lab(hh$total) = make_labels(" 
                                  1
                                ")
val_lab(hh$total100) = make_labels("
                                   100
                                   ")


```







# 10.1.1 Table




```{r}


tab.1.1 = xtabs(nhhmem ~ WS1, hh) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH6) + WS1, hh)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH7) + WS1, hh)) %>%
  rbind(xtabs(nhhmem ~ as_factor(helevel) + WS1, hh)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(windex5) + WS1, hh))


tab.improved = xtabs(nhhmem ~ improvedWater, hh) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH6) + improvedWater, hh)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH7) + improvedWater, hh)) %>%
  rbind(xtabs(nhhmem ~ as_factor(helevel) + improvedWater, hh)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(windex5) + improvedWater, hh))


tab.1.1 = tab.1.1 %>%
  cbind(Total = rowSums(tab.1.1)) %>% 
  cbind(tab.improved[, 2])

N = round(tab.1.1[ , 17])

colnames(tab.1.1)[18] = "Percentage using drinking water from improved sources"



#labels(tabf)[[1]][1] = "Total"
tab.1.1 = apply(tab.1.1, 2, function(x) (x*100) / tab.1.1[, 17])

tab.1.1 <- tab.1.1 %>% cbind(N); colnames(tab.1.1)[18:19] = c("Pourcen-tage utilisant de l'eau de boisson de sources améliorées1", "Nombre de membres des ménages ")

rownames(tab.1.1)[1] = "Total"





# columns are labeled incorrectly 
# SPSS syntax does not match table output, even though I get correct results, they are nested in 
# incorrect value labels / label hierarchies, can fix this as I go, need to investigate though

ind <- c(1, 2, 3, 4, 5, 6, 8, 10, 11, 12, 14, 15, 7, 9, 13, 16, 17)

tab.1.1[ , 1:17] = tab.1.1[ , ind]

colnames(tab.1.1)[1:17] = colnames(tab.1.1)[ind]

```




# SFR Table Ch10 WS 1.1


```{r, echo = T, eval = T}

tab.1.1 %>% 
  kable(format = "latex", digits = 1, format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kable_styling(c("striped"), font_size = 11) %>% 
#  pack_rows("Total", 1, 1) %>% 
  pack_rows(label(hh$HH6), 2, 3) %>% 
  pack_rows(label(hh$HH7), 4, 10) %>% 
  pack_rows(label(hh$helevel), 11, 15) %>% 
  pack_rows(label(hh$windex5), 16, 20) %>% 
  add_header_above(c(" " , "Eau courante" = 4, " " = 15)) %>% 
  add_header_above(c(" ", "Sources améliorées" = 12, "Sources non améliorées" = 4, " " = 3)) %>% 
  add_header_above(c(" ", "Source principale d'eau de boisson" = 19))


a = data.frame(tab.1.1); 

a = lapply(a, function(x) round(x, digits = 1)) %>% data.frame(); colnames(a) = colnames(tab.1.1)
rownames(a) = rownames(tab.1.1)

aa = colnames(a)


ft = flextable(a %>% rownames_to_column(" ")) %>% autofit() %>% 
  fontsize(part = "all", size = 4) %>% bold(part = "header") %>% 
  add_header(`DANS LE LOGEMENT` = "Eau courante",
             `DANS LA CONCESSION/JARDIN/ PARCELLE` = "Eau courante",
             `CHEZ LE VOISIN` = "Eau courante",
             `ROBIENT PUBLIC/BORNE FONTAINE` = "Eau courante") %>% 
  add_header(
  `DANS LE LOGEMENT` = "Sources améliorées",
  `DANS LA CONCESSION/JARDIN/ PARCELLE` = "Sources améliorées",
  `CHEZ LE VOISIN` = "Sources améliorées",
  `ROBIENT PUBLIC/BORNE FONTAINE` = "Sources améliorées", 
  `PUITS A POMPE/FORAGE` = "Sources améliorées",
  `PROTEGE` = "Sources améliorées",
  `SOURCE PROTEGEE` = "Sources améliorées",
  `EAU DE PLUIE` = "Sources améliorées",
  `CAMION CITERNE` = "Sources améliorées",
  `CHARRETTE AVEC PETITE CITERNE` = "Sources améliorées",
  `EAU EN BOUTEILLE` = "Sources améliorées",
  `EAU EN SACHET` = "Sources améliorées",
  `PAS PROTEGE` = "Sources non améliorées",
  `SOURCE NON PROTEGEE` = "Sources non améliorées",
  `EAU DE SURFACE (RIVIERE, BARRAGE, LAC, MARE, COURANT, CANAL, SYSTEME D’IRRIGATION)` = "Sources non améliorées",
  `AUTRE` = "Sources non améliorées"
  ) %>% 
  add_header(
  `DANS LE LOGEMENT` = "Source principale d'eau de boisson",
  `DANS LA CONCESSION/JARDIN/ PARCELLE` = "Source principale d'eau de boisson",
  `CHEZ LE VOISIN` = "Source principale d'eau de boisson",
  `ROBIENT PUBLIC/BORNE FONTAINE` = "Source principale d'eau de boisson", 
  `PUITS A POMPE/FORAGE` = "Source principale d'eau de boisson",
  `PROTEGE` = "Source principale d'eau de boisson",
  `SOURCE PROTEGEE` = "Source principale d'eau de boisson",
  `EAU DE PLUIE` = "Source principale d'eau de boisson",
  `CAMION CITERNE` = "Source principale d'eau de boisson",
  `CHARRETTE AVEC PETITE CITERNE` = "Source principale d'eau de boisson",
  `EAU EN BOUTEILLE` = "Source principale d'eau de boisson",
  `EAU EN SACHET` = "Source principale d'eau de boisson",
  `PAS PROTEGE` = "Source principale d'eau de boisson",
  `SOURCE NON PROTEGEE` = "Source principale d'eau de boisson",
  `EAU DE SURFACE (RIVIERE, BARRAGE, LAC, MARE, COURANT, CANAL, SYSTEME D’IRRIGATION)` = "Source principale d'eau de boisson",
  `AUTRE` = "Source principale d'eau de boisson"
  ) %>% 
  merge_h(i = 1:3, part = "header") %>% 
  theme_zebra() %>% 
  align(align = "center", part = "all") %>% fontsize(part = "header", size = 5)
  #border_inner_v(part = "all", border = fp_border(color = "gray")) %>% fix_border_issues()
 
 
 
 
   

#  add_header(`DANS LE LOGEMENT` = "Eau courante",
#             `DANS LA CONCESSION/JARDIN/ PARCELLE` = "Eau courante",
#             `CHEZ LE VOISIN` = "Eau courante",
#             `ROBIENT PUBLIC/BORNE FONTAINE` = "Eau courante") 

FitFlextableToPage <- function(ft, pgwidth = 8){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

 FitFlextableToPage(ft, pgwidth = 8)



```









# 10 - WS.1.2


Reminder: change ALL case whens into nested ifelse, case_when function just burned 
me on 1.2 table...

```{r}

hh <- read_sav(here("Data/Tunisia_hh.sav"))

hh <- hh %>% filter(HH46 == 1) %>% mutate(hhweightHH48 = HH48 * hhweight) %>% 
  mutate(nhhmem = 1 * hhweightHH48)

var_lab(hh$nhhmem) = "Number of household members"; val_lab(hh$nhhmem) = make_labels("
                                                                                     1
                                                                                     ")
# reload data as start over as in SPS syntax file

hh <- hh %>% mutate(time = ifelse(WS4 %in% 0:30, 2, 
                                  ifelse(WS4 %in% 31:990, 3,
                                         ifelse(WS4 %in% c(998, 999), 9,
                                                WS4)))) %>% 
  mutate(time = ifelse(WS1 %in% 11:13 |
                         WS2 %in% 11:13 |
                         WS3 %in% 1:2, 1, time))




var_lab(hh$time) = "Time to source of drinking water"; val_lab(hh$time) = make_labels(" 
    1 Water on premises
    2 Up to and including 30 minutes [A]
    3 More than 30 minutes
    9 DK/Missing
    ")


#####################      BEGIN 10 - WS.SPS    ################################


hh <- hh %>% 
  mutate(drinkingWater = ifelse(WS1 %in% c(11:14, 21, 31, 41, 51, 61, 71, 72, 91, 92), 1, 2))

var_lab(hh$drinkingWater) = "Main source of drinking water"
val_lab(hh$drinkingWater) = make_labels("
  1 Improved sources
  2 Unimproved sources
")



hh <- hh %>% 
  mutate(toiletType = case_when(
    WS11 %in% c(11:13, 18, 21, 22, 31) ~ 1,
    WS11 == 95 ~ 3,
    TRUE ~ 2
  ))


var_lab(hh$toiletType) = "Type of sanitation facility"
val_lab(hh$toiletType) = make_labels("
    1 Improved
    2 Unimproved
    3 Open defecation (no facility, bush, field)
                                     ")


hh <- hh %>% mutate(flush = NA) %>% mutate(flush = case_when(
  WS11 %in% c(1:14, 18) ~ 1
))

var_lab(hh$flush) = ""; val_lab(hh$flush) = make_labels(" 
                                                        1 Flush/Pour flush to:
                                                        ")



hh <- hh %>% mutate(sharedToilet = case_when(
  WS17 %in% c(1:5) ~ 1,
  WS17 %in% 97:99 ~ 9,
  NA ~ 0,
  TRUE ~ 2
))

hh <- hh %>% mutate(sharedToilet = ifelse(WS16 == 2, 3, sharedToilet))

var_lab(hh$sharedToilet) = " "
val_lab(hh$sharedToilet) = make_labels("
  0 Not shared
  1 5 households or less
  2 More than 5 households
  3 Public facility
  9 DK/Missing
                                       ")


#####################     END 10 - WS.SPS      ################################

var_lab(hh$drinkingWater) = "Time to source of drinking Water"
val_lab(hh$drinkingWater) = make_labels("
      1 Users of improved drinking water sources 
      2 Users of unimproved drinking water sources
                                        ")

hh <- hh %>% 
  mutate(INDWS2 = 0) %>% 
  mutate(INDWS2 = case_when(
    WS1 %in% c(11, 12) ~ 100,
    (WS1 %in% c(61, 71, 72)) & (WS4 <= 30) ~ 100,
    (WS1 %in% c(13, 14, 21, 31, 41, 51)) & (WS3 %in% 1:2 | WS4 <= 30) ~ 100,
    (WS1 %in% 91:92) & (WS2 %in% 11:12) ~ 100,
    (WS1 %in% 91:92) & (WS2 %in% c(61, 71, 72) & WS4 <= 30) ~ 100,
    (WS1 %in% 91:92) & (WS2 %in% c(13, 14, 21, 31, 41, 51)) & (WS3 %in% 1:2 | WS4 <= 30) ~ 100
  )  )

hh$total = 1
var_lab(hh$INDWS2) = "Percentage using basic drinking water services [1]"
var_lab(hh$total) = "Total"; val_lab(hh$total) = make_labels("
                                                             1 
                                                             ")



```





## 10.1.2 Tables




The general code process for creating the tables in R is as follows: 
(there may be a more clever way to do this in one table command, but this works for now)

Each `xtabs` command computes a contingency table
We go group by group - so e.g. starting off with contingency table of `HH6` (Area) 
vs. `WS1` (drinking water source) , or for 1.2 Area vs `time` 

This one `xtabs` command is a single building block in our SFR table, we then stack these downwards
using the `rbind` command in R, which "rowbinds" blocks together. 

Naturally - Using `rbind` to rowbind two objects together (table / dataframe / list etc) requires
exact same columns in each object, similarly `cbind` (column binding) two objects requires exact same
rows

We rowbind together downwards - `HH6` - Area, `HH7` Region, `helevel` education level, and `windex5`
wealth quintile. For the table here in 1.2, there's an additional step of performing this sequence 
on a filtered dataframe for `drinkingWater == 1`, then using `cbind` to bind together
the same table but for `drinkingWater == 2`


```{r}

df.unweighted <- hh %>% summarize(Count = sum(HH48)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(HH6)) %>% 
                     summarize(Count = sum(HH48)) %>% select(Count)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(HH7)) %>% 
                     summarize(Count = sum(HH48)) %>% select(Count)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(helevel)) %>% 
                     summarize(Count = sum(HH48)) %>% select(Count)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(windex5)) %>% 
                     summarize(Count = sum(HH48)) %>% select(Count)); 

df.unweighted$Count = round(df.unweighted$Count); 
rownames(df.unweighted) = c("Total", levels(as_factor(hh$HH6)), levels(as_factor(hh$HH7)), levels(as_factor(hh$helevel)), 
                levels(as_factor(hh$windex5)))




# to be turned into function - this is likely common task in every chapter...
N <- hh %>% summarize(Count = sum(nhhmem)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(HH6)) %>% 
                     summarize(Count = sum(nhhmem)) %>% select(Count)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(HH7)) %>% 
                     summarize(Count = sum(nhhmem)) %>% select(Count)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(helevel)) %>% 
                     summarize(Count = sum(nhhmem)) %>% select(Count)) %>% 
  rbind.data.frame(hh %>% group_by(as_factor(windex5)) %>% 
                     summarize(Count = sum(nhhmem)) %>% select(Count)); 

N$Count = round(N$Count)
N <- N %>% mutate(Total = Count)
N <- data.frame(N); colnames(N)[1] = c("Number of household members")
rownames(N) = c("Total", levels(as_factor(hh$HH6)), levels(as_factor(hh$HH7)), levels(as_factor(hh$helevel)), 
                levels(as_factor(hh$windex5)))




tab.improved = xtabs(nhhmem ~ as_factor(time), hh %>% filter(drinkingWater == 1)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH6) + as_factor(time), hh %>% filter(drinkingWater == 1))) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH7) + as_factor(time), hh %>% filter(drinkingWater == 1))) %>%
  rbind(xtabs(nhhmem ~ as_factor(helevel) + as_factor(time), hh %>% filter(drinkingWater == 1))) %>% 
  rbind(xtabs(nhhmem ~ as_factor(windex5) + as_factor(time), hh %>% filter(drinkingWater == 1)))


tab.unimproved = xtabs(nhhmem ~ as_factor(time), hh %>% filter(drinkingWater == 2)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH6) + as_factor(time), hh %>% filter(drinkingWater == 2))) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH7) + as_factor(time), hh %>% filter(drinkingWater == 2))) %>%
  rbind(xtabs(nhhmem ~ as_factor(helevel) + as_factor(time), hh %>% filter(drinkingWater == 2))) %>% 
  rbind(xtabs(nhhmem ~ as_factor(windex5) + as_factor(time), hh %>% filter(drinkingWater == 2)))


tab.basic = xtabs(nhhmem ~ as_factor(INDWS2), hh) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH6) + as_factor(INDWS2), hh)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(HH7) + as_factor(INDWS2), hh)) %>%
  rbind(xtabs(nhhmem ~ as_factor(helevel) + as_factor(INDWS2), hh)) %>% 
  rbind(xtabs(nhhmem ~ as_factor(windex5) + as_factor(INDWS2), hh))


tab.1.2 = cbind(tab.improved, tab.unimproved, N$Total, tab.basic, N$`Number of household members`)



tab.1.2 = apply(tab.1.2[ , 1:(ncol(tab.1.2)-1)], 2, function(x) (x * 100) / tab.1.2[ , ncol(tab.1.2) - 2]) %>% cbind(N$`Number of household members`)

colnames(tab.1.2)[(ncol(tab.1.2) - 2):ncol(tab.1.2)] = c("Total",
                            "Percentage using basic drinking water services [1]",
                            "Number of household members")



rownames(tab.1.2)[1] = "Total"





```



### parenth function

```{r}

paren_fun <- function(df) {
  df <- df %>% mutate(less_25 = ifelse(Count <= 25, 1, ))
}


```



# SFR Table Ch10 WS 1.2



```{r, eval = T}

header1 = label(hh$time)

tab.1.2 %>% 
  kable(digits = 1, format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kable_styling(c("striped"), font_size = 12) %>% 
  pack_rows(label(hh$HH6), 2, 3) %>% 
  pack_rows(label(hh$HH7), 4, 10) %>% 
  pack_rows(label(hh$helevel), 11, 15) %>% 
  pack_rows(label(hh$windex5), 16, 20) %>% 
  add_header_above(c(" ", "Users of improved drinking water sources" = 4, 
                     "Users of unimproved drinking water sources" = 4,
                     " " = 3)) %>% 
  add_header_above(c(" ", "Time to source of drinking water" = 8, " " = 3))
  



```




```{r}


a = data.frame(tab.1.2); 

a = lapply(a, function(x) round(x, digits = 1)) %>% data.frame(); colnames(a) = colnames(tab.1.2)
rownames(a) = rownames(tab.1.2)
colnames(a)[5:8] = c(" Water on premises", " Up to and including 30 minutes [A]",
                     " More than 30 minutes", " DK/Missing")
aa = colnames(a)


ft = flextable(a %>% rownames_to_column(" ")) %>% autofit() %>% 
  fontsize(part = "all", size = 4) %>% bold(part = "header") %>% 
  add_header(`Water on premises` = "Users of improved drinking water sources",
             `Up to and including 30 minutes [A]` = "Users of improved drinking water sources",
             `More than 30 minutes` = "Users of improved drinking water sources",
             `DK/Missing` = "Users of improved drinking water sources",
             ` Water on premises` = "Users of unimproved drinking water sources",
             ` Up to and including 30 minutes [A]` = "Users of unimproved drinking water sources",
             ` More than 30 minutes` = "Users of unimproved drinking water sources",
             ` DK/Missing` = "Users of unimproved drinking water sources") %>% 
add_header(
             `Water on premises` = "Time to source of drinking water",
             `Up to and including 30 minutes [A]` = "Time to source of drinking water",
             `More than 30 minutes` = "Time to source of drinking water",
             `DK/Missing` = "Time to source of drinking water",
             ` Water on premises` = "Time to source of drinking water",
             ` Up to and including 30 minutes [A]` = "Time to source of drinking water",
             ` More than 30 minutes` = "Time to source of drinking water",
             ` DK/Missing` = "Time to source of drinking water"
) %>% 
  merge_h(i = 1:3, part = "header") %>% 
  theme_zebra() %>% 
  align(align = "center", part = "all") %>% fontsize(part = "header", size = 5)
  #border_inner_v(part = "all", border = fp_border(color = "gray")) %>% fix_border_issues()
 
 
 
 
   

#  add_header(`DANS LE LOGEMENT` = "Eau courante",
#             `DANS LA CONCESSION/JARDIN/ PARCELLE` = "Eau courante",
#             `CHEZ LE VOISIN` = "Eau courante",
#             `ROBIENT PUBLIC/BORNE FONTAINE` = "Eau courante") 

FitFlextableToPage <- function(ft, pgwidth = 8){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}

 FitFlextableToPage(ft, pgwidth = 8)

```




# flextables experimentation

```{r, eval = F}

a = data.frame(tab.1.1); 

a = lapply(a, function(x) round(x, digits = 1)) %>% data.frame(); colnames(a) = colnames(tab.1.1)
rownames(a) = rownames(tab.1.1)

flextable(a %>% rownames_to_column("a"), col_keys = names(a)) %>% autofit() %>% 
  add_header_lines("Users of improved drinking water sources") %>% 
  fontsize(part = "header", size = 14) %>% bold(part = "header") %>% 
  border_inner_v(border = fp_border(color = "gray"), part = "all")


aa = colnames(a)

flextable(a %>% rownames_to_column(" ")) %>% autofit() %>% 
  fontsize(part = "header", size = 10) %>% bold(part = "header") %>% 
  fontsize(part = "body", size = 7) %>% 
  add_header(`DANS LE LOGEMENT` = "Eau courante") %>% 
  merge_at(i = 1, j = 2:4, part = "header") %>% 
  add_header(`PROTEGE` = "Sources améliorées",
             `AUTRE` = "Sources non améliorées") %>% 
 # merge_at(i = 1, j = 5:12, part = "header") %>% 
  add_header(`CAMION CITERNE` = "Source principale d'eau de boisson") %>% 
  border_inner_v(border = fp_border(color = "gray")) %>% theme_zebra()


```

```{r, eval = F}

flextable(a) %>% set_header_df(mapping = b, key = "col_keys")

ft <- flextable( head( iris ) ); ft
ft <- add_footer_lines(ft, values = "blah blah"); ft
ft <- add_footer_lines(ft, values = c("blah 1", "blah 2"))
autofit(ft)
ft <- flextable( head( iris ) ); ft
ft <- add_header_lines(ft, values = "blah blah"); ft
ft <- add_header_lines(ft, values = c("blah 1", "blah 2")); ft
autofit(ft)


```



```{r, eval = F}

atypology <- data.frame(
  col_keys = colnames(a),
  what = c(rep("a", 4), rep(" ", 15)), stringsAsFactors = FALSE)


typology <- data.frame(
  col_keys = c( "Sepal.Length", "Sepal.Width", "Petal.Length",
                "Petal.Width", "Species" ),
  what = c("Sepal", "Sepal", "Petal", "Petal", "Species"),
  measure = c("Length", "Width", "Length", "Width", "Species"),
  stringsAsFactors = FALSE )

ft <- flextable( head( iris ))
ft <- set_header_df(ft, mapping = typology, key = "col_keys" )
ft <- merge_h(ft, part = "header")
ft <- merge_v(ft, j = "Species", part = "header")
ft <- theme_vanilla(ft)
ft

typology <- data.frame(
  col_keys = c( "Sepal.Length", "Sepal.Width", "Petal.Length",
                "Petal.Width", "Species" ),
  unit = c("(cm)", "(cm)", "(cm)", "(cm)", ""),
  stringsAsFactors = FALSE )
ft <- set_footer_df(ft, mapping = typology, key = "col_keys" )
ft <- italic(ft, italic = TRUE, part = "footer" )
ft <- theme_booktabs(ft)
ft
```

