---
title: "MICS6 - 10 - WS.1.1"
author: "Reid Minto"
date: "March 25, 2020"
output: github_document
always_allow_html: true
---

# Load libraries





```{r, warning = F, message = F}

library(tidyverse); library(haven); library(lubridate);
library(knitr); library(kableExtra)
library(Hmisc); library(survey)
library(expss); library(here); library(gmodels)
library(flextable); library(formattable)
library(prettydoc)

library(tableone); library(sjPlot); library(srvyr)

```
 
# Import data

`here` function navigates you to top level Rproj directory



```{r}
# haven library called above has read_sav function for reading in .sav / .sps etc
# files from other languages
here()
hh <- read_sav(here("Data/Tunisia_hh.sav"))
# hh <- as_factor(hh, only_labelled = TRUE)




```

Filter only cases where hh interview = 1, create a variable `hhweightHH48` by multiplying 
`HH48` and `hhweight`, number of hh members by sample weight


Note: this is just first pass rough draft / run through - much of this looks like it can be consolidated into a single chunk / a single function execute per section from what I've seen so far, but broken up in first pass

```{r}

hh <- hh %>% filter(HH46 == 1) %>%
  mutate(hhweightHH48 = HH48 * hhweight,
         nhhmem = 1)


```

Include `MICS6 - 10 - WS.sps` is called



```{r}


hh <- hh %>% 
  mutate(drinkingWater = ifelse(WS1 %in% 
                                  c(11:14, 21, 31, 41, 51, 61, 71, 72, 91, 92),
                                1, 2))

# `casewhen` cleaner than nested chains of ifelse for >2 conditions
# same as SQL 'case when', but TRUE ~ val acts in place of "else"
hh <- hh %>%
  mutate(toiletType = case_when(
    WS11 %in% c(11:13, 18, 21, 22, 31) ~ 1,
    WS11 == 95 ~ 3,
    TRUE ~ 2
  ))
  


hh <- hh %>% 
  mutate(flush = NA) %>% 
  mutate(flush = ifelse(WS11 %in% c(11:14, 18), 1, flush))



hh = hh %>% mutate(sharedToilet = case_when(
  WS17 %in% c(1:5) ~ 1,
  WS17 %in% 97:99 ~ 9,
  is.na(WS17) ~ 0,
  TRUE ~ 2))

hh = hh %>% mutate(sharedToilet = ifelse(WS16 == 2, 3, sharedToilet))


# visual check
aa = hh %>% 
  select(WS1, HH1, HH2, nhhmem, hhweightHH48, hhweight, 
         HH48, stratum, PSU, drinkingWater, WS11)

```



After 10-WS include file call, resume

## Include 10 - WS

```{r}

hh <- hh %>% 
  mutate(improvedWater = ifelse(drinkingWater == 1, 100, 0),
         total = 1,
         total100 = 100)




```




# All Value labels

Variable and Value labels all at once

Question if this is necessary at all in R, b/c can just as easily label R tables / figured with a list of labels when generating the tables / figures / reports, avoiding doing as we go along. 



```{r}

hh <- hh %>% apply_labels(
  nhhmem = "Number of household members",
  WS1 = c(
#  "Tanker Truck" = 61, 
#  "Cart with small tank" = 71, 
#  "Bottled water [A]" = 91,  
#  "Sachet water [A]" = 92, 
#  "Missing" = 99,
  # not in SPS syntax, only in CSPro SPS file.... 
  "ROBINET: DANS LE LOGEMENT" =   11,
   "ROBINET: DANS LA CONCESSION/JARDIN/ PARCELLE" = 12, 
    "ROBINET: CHEZ LE VOISIN" = 13,
    "ROBINET: ROBIENT PUBLIC/BORNE FONTAINE" = 14,
     "PUITS A POMPE/FORAGE" = 21,
     "PUITS CREUSE: PROTEGE" = 31,
     "PUITS CREUSE: PAS PROTEGE" = 32,
     "SOURCE: SOURCE PROTEGEE" = 41,
     "SOURCE: SOURCE NON PROTEGEE" = 42,
     "EAU DE PLUIE" = 51,
     "CAMION CITERNE" = 61,
     "CHARRETTE AVEC PETITE CITERNE" = 71,
    "EAU DE SURFACE (RIVIERE, BARRAGE, LAC, MARE, COURANT, CANAL, SYSTEME D’IRRIGATION)" = 81,
    "EAU CONDITIONNEE: EAU EN BOUTEILLE" = 91,
    "EAU CONDITIONNEE: EAU EN SACHET" = 92,
    "AUTRE" = 96,
    "NON REPONSE" = 99),
  
  
  drinkingWater = "Main Source of drinking water",
  drinkingWater = c(
    "Improved sources" = 1,
    "Unimproved sources" = 2
    ),
  toiletType = "Type of sanitation facility",
  toiletType = c(
    "Improved" = 1,
    "Unimproved" = 2,
    "Open defecation (no facility, bush, field)" = 3
    ),
  flush = "Flush/Pour flush to:",
  sharedToilet = c(
    "Not shared" = 0,
    "5 households or less" = 1,
    "More than 5 households" = 2,
    "Public facility" = 3,
    "DK/Missing" = 9
  ),
  improvedWater = "Percentage using improved sources of drinking water [1]",
  HH6 = c("URBAN" = 1, "RURAL" = 2)


  
  
  )




# hh <- as_factor(hh, only_labelled = TRUE)






```


# Tables






```{r}

hh.tab <- hh %>% 
  mutate(nn = nhhmem * hhweightHH48) %>% 
  select(WS1, HH6, HH7, helevel, windex5, drinkingWater, total100, total, improvedWater, 
         nhhmem, nn)

# convert sps labels to factor labels in r
hh.tab = as_factor(hh.tab, only_labelled = TRUE)
hh = hh %>% mutate(nn = nhhmem * hhweightHH48)

tab.total = hh %>% tally(nn, name = "Count")

tab = tab.total %>% 
  rbind.data.frame(
    hh.tab %>% group_by(HH6) %>% tally(nn, name = "Count") %>% select(Count),
    hh.tab %>% group_by(HH7) %>% tally(nn, name = "Count") %>% select(Count),
    hh.tab %>% group_by(helevel) %>% tally(nn, name = "Count") %>% select(Count),
    hh.tab %>% group_by(windex5) %>% tally(nn, name = "Count") %>% select(Count)
  ) %>% data.frame()


row.names(tab) = c("Total", levels(hh.tab$HH6), levels(hh.tab$HH7), 
                   levels(hh.tab$helevel), levels(hh.tab$windex5))


#kable(tab, digits = 0) %>% 
#  kable_styling("striped") %>% 
#  pack_rows("Total", 1, 1) %>% 
#  pack_rows(label(hh.tab$HH6), 2, 3) %>% 
#  pack_rows(label(hh.tab$HH7), 4, 10) %>% 
#  pack_rows(label(hh.tab$helevel), 11, 15) %>% 
#  pack_rows(label(hh.tab$windex5), 16, 20)



N <- tab$Count
df.tab = data.frame(tab)


```


# 10.1.1 Table

```{r, echo=F}

kable(tab, digits = 0) %>% 
  kable_styling("striped") %>% 
  pack_rows("Total", 1, 1) %>% 
  pack_rows(label(hh.tab$HH6), 2, 3) %>% 
  pack_rows(label(hh.tab$HH7), 4, 10) %>% 
  pack_rows(label(hh.tab$helevel), 11, 15) %>% 
  pack_rows(label(hh.tab$windex5), 16, 20)

```

```{r}

tab2 = table(c(hh.tab$HH6, hh.tab$HH7, hh.tab$helevel, hh.tab$windex5), c(rep(hh.tab$WS1, 4)))
tab2 = table(c(hh$HH6, as_factor(hh$HH7), hh$helevel, 
               hh$windex5), c(rep(hh$WS1, 4)))

kable(tab2, digits = 0) %>% 
  kable_styling("striped")



```



```{r}


tabf = xtabs(nn ~ WS1, hh) %>% 
  rbind(xtabs(nn ~ HH6 + WS1, hh)) %>% 
  rbind(xtabs(nn ~ as_factor(HH7) + WS1, hh)) %>%
  rbind(xtabs(nn ~ as_factor(helevel) + WS1, hh)) %>% 
  rbind(xtabs(nn ~ as_factor(windex5) + WS1, hh))

tabf = tabf %>% cbind(Total = rowSums(tabf))
#labels(tabf)[[1]][1] = "Total"
tab.final = apply(tabf, 2, function(x) (x*100) / tabf[, 17]) %>% cbind(round(df.tab$Count))




tabf.rows = labels(tabf)[[1]]
tabf.cols = labels(tabf)[[2]]





```

# SFR Table ch10 WS 1.1


```{r}

tab.final %>% 
  kable(digits = 1, format.args = list(big.mark = ",", scientific = FALSE)) %>% 
  kable_styling(c("striped"), font_size = 13) %>% 
  pack_rows("Total", 1, 1) %>% 
  pack_rows(label(hh.tab$HH6), 2, 3) %>% 
  pack_rows(label(hh.tab$HH7), 4, 10) %>% 
  pack_rows(label(hh.tab$helevel), 11, 15) %>% 
  pack_rows(label(hh.tab$windex5), 16, 20) %>% 
  add_header_above(c(" " , "Eau courante" = 4, " " = 14)) %>% 
  add_header_above(c(" ", "Sources améliorées" = 12, "Sources non améliorées" = 4, " " = 2)) %>% 
  add_header_above(c(" ", "Source principale d'eau de boisson" = 18))


```

# 10.1.2

Recode WS4


Odd that 1.2 syntax file has variable label for drinkingWater
exact same as time var label....


```{r}

hh <- hh %>% 
  mutate(
    time = case_when(
    WS4 %in% 0:30 ~ 2,
    WS4 %in% 31:990 ~ 3,
    WS4 %in% 998:999 ~ 9,
    WS1 %in% 11:13 | WS2 %in% 11:13 | WS3 %in% 1:2 ~ 1
    )) %>% 
  mutate(INDWS2 = 0) %>% 
  mutate(INDWS2 = case_when(
    WS1 %in% c(11, 12) ~ 100,
    WS1 %in% c(61, 71, 72) & WS4 <= 30 ~ 100,
    WS1 %in% c(13, 14, 21, 31, 41, 51) & WS3 %in% 1:2 | WS4 <= 30 ~ 100,
    WS1 %in% 91:92 & WS2 %in% 11:12 ~ 100,
    WS1 %in% 91:92 & (WS2 %in% c(61, 71, 72) & WS4 <= 30) ~ 100,
    WS1 %in% 91:92 & WS2 %in% c(13, 14, 21, 31, 41, 51) & 
      (WS3 %in% 1:2 | WS4 <= 30) ~ 100
  )  )


```



## 10.1.2 Labels


```{r}

hh <- hh %>% 
  apply_labels(
    time = "Time to source of drinking water",
    time = c(
      "Water on premises" = 1,
      "Up to and including 30 minutes [A]" = 2,
      "More than 30 minutes" = 3,
      "DK/Missing" = 9
    ),
    drinkingWater = "Time to source of drinking water",
    drinkingWater = c(
      "Users of improved drinking water sources" = 1,
      "Users of unimproved drinking water sources" = 2
    ),
    INDWS2 = "Percentage using basic drinking water services [1]"
    
  )
  

```



## 10.1.2 Tables

```{r, eval = F}
ctables
  /vlabels variables = time
           display = none
  /table   total [c]
         + HH6 [c]
         + HH7 [c]
         + helevel [c]
         + ethnicity [c]
         + windex5 [c]
   by
           drinkingWater [c] >
             time[c][layerrowpct.validn '' f5.1]
         + total100 [s] [mean '' f5.1]
         + INDWS2 [s] [mean '' f5.1]
         + nhhmem [s] [count '' f5.0]
  /categories variables=all empty=exclude missing=exclude
```

