---
title: "test"
author: "Reid Minto"
date: "2/17/2020"
output: html_document
---

# Load libraries and Import data 

```{r, warning = F, message = F}

library(tidyverse); library(lubridate);
library(survey); library(RCurl)


df <- mtcars

```


Suppose we're running through a routine or analysis and we want to apply some calculation or function to our dataset `df` , and what we want to do is fairly routine so we have wrapped it up into a custom function that we apply to our unicef routines systematically....

__Any__ analyst at Unicef that uses R and would find some utility in wrapping up their frequent calculations / tasks etc. into a helper function could make use of sourcing the functions from our github page, e.g. for simplicity suppose I just want to see how many NAs / nulls are in every column for a dataset with 300 columns for example. 



```{r}

# source our helper function from our github page


source("https://raw.github.com/rminto/Blog-Reference-Functions/master/R/bingSearchXScraper/bingSearchXScraper.R")

```

