---
title: "SPSS to R"
author: "Reid Minto"
date: "March 30, 2020"
output:
  word_document: default
  html_document: default
---

# Libraries

```{r global_options}


knitr::opts_chunk$set(eval = F)



```

`select if (HH46  = 1).`

`select if` is SPSS version of `filter` for subsetting in R, based on
`filter(expr)`

```{r}

df %>% filter(var == value)

```

```{r}

# To convert into spss to R functions



compute hhweightHH48 = HH48*hhweight.
# df %>% mutate(hhweightHH48 = HH48 * hhweight)

variable labels  total100 "Total".
# variable labels are attribute labels


value labels total100 100 " ".
# value labels are just string categories assigned to coded values of a variable
hh <- hh %>% apply_labels(
  nhhmem = "Number of household members",
  WS1 = c(
    "Tanker Truck" = 61, 
    "Cart with small tank" = 71, 
    "Bottled water [A]" = 91,  
    "Sachet water [A]" = 92, 
    "Missing" = 99),
  


```

do if any(WS1, 11, 12, 13, 14, 21, 31, 41, 51, 61, 71, 72,  91, 92) .
+ compute drinkingWater = 1 .
else .
+ compute drinkingWater = 2 .
end if.
```{r}

# create new variable that's just using ifelse for conditional evaluation 
# based on values of var already in dataset
```


# ctables

ctables
  /vlabels variables = WS1
           display = none
  /table   total [c]
         + HH6 [c]
         + HH7 [c]
         + helevel [c]
         + ethnicity [c]
         + windex5 [c]
   by 
           drinkingWater [c] > 
             ws1 [c] [layerrowpct.validn,' ',f5.1]
         + total100 [s] [mean '' f5.1] 
         + improvedWater [s] [mean '' f5.1] 
         + nhhmem [s] [count '' f5.0] 

```{r}



```



